Supermassive black hole and host bulge affairs \\ I. True to life galaxy decomposition.

### 2015-06-16 papers/data_paper/datapaper.tex
martedi arcetri

  OK

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/m104_1Dfit.eps}
  \caption{Best-fit model and isophotal parameters for M104.}
  \end{center}
  \end{figure}

@@

  \begin{table}[h]
  \small
  \caption{Best-fit parameters for the spheroidal component of NGC 3377.}
  \begin{center}
  \begin{tabular}{llcc}
  \hline
  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
    &  &  $[\rm arcsec]$ & \\
  \hline
  T.W. 1D maj. & S-bul + 2 e-id     & $61.8$  &  $7.7$ \\
  T.W. 1D eq.  & S-bul + 2 e-id     & $91.7$  &  $9.2$ \\
  T.W. 2D      & S-bul + e-id + m-n & $71.8$  &  $3.7$ \\
  \hline
  GD07         & S-bul     		     & $44.1$  &  $3.0$ \\
  S+11         & S-bul     		     & $55.2$  &  $6.0$ \\
  B+12         & S-bul     		     & $43.5$  &  $3.5$ \\
  L+14         & S-bul + e-id + e-d + S-halo & $10.1$  &  $6.0$ \\
  \hline
  \end{tabular}
  \end{center}
  \label{tab:n3377}
  \end{table}

>>>>

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/m104_1Dfit.eps}
  \caption{Best-fit model and isophotal parameters for M104.
  }
  \end{center}
  \end{figure}

  \begin{table}[h]
  \small
  \caption{Best-fit parameters for the spheroidal component of M104.}
  \begin{center}
  \begin{tabular}{llcc}
  \hline
  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
    &  &  $[\rm arcsec]$ & \\
  \hline
  T.W. 1D maj. & S-bul + e-d + G-r + m-c  & $11.1$  &  $5.4$ \\
  T.W. 1D eq.  & S-bul + e-d + G-r + m-c  & $52.5$  &  $7.1$ \\
  \hline
  S+11         & S-bul + e-d + G-bar + G-n  & $66.1$  &  $1.5$ \\
  \hline
  \end{tabular}
  \end{center}
  \label{tab:m104}
  \tablecomments{The bulge S\'ersic index obtained by S+11 is smaller than our estimates because 
  they fit a nuclear component. }
  \end{table}

@@

  \begin{table}[h]
  \small
  \caption{Best-fit parameters for the spheroidal component of NGC 3377.}
  \begin{center}
  \begin{tabular}{llcc}
  \hline
  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
    &  &  $[\rm arcsec]$ & \\
  \hline
  T.W. 1D maj. & S-bul + 2 e-id     & $61.8$  &  $7.7$ \\
  T.W. 1D eq.  & S-bul + 2 e-id     & $91.7$  &  $9.2$ \\
  T.W. 2D      & S-bul + e-id + m-n & $71.8$  &  $3.7$ \\
  \hline
  GD07         & S-bul     		     & $44.1$  &  $3.0$ \\
  S+11         & S-bul     		     & $55.2$  &  $6.0$ \\
  B+12         & S-bul     		     & $43.5$  &  $3.5$ \\
  L+14         & S-bul + e-id + e-d + S-halo & $10.1$  &  $6.0$ \\
  \hline
  \end{tabular}
  \end{center}
  \label{tab:n3377}
  \tablecomments{L+14 obtained the smallest estimate of the effective radius because they oversubtracted a halo.   
  }
  \end{table}
